Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador \newline \newline Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra del \'{a}rea Metropolitana de San Salvador, El Salvador

### 2015-06-06 paper.tex
06 June 2015 11:05

%In order to make spatial predictions using ordinary kriging, a R script was developed which can be accessed in the following web address: 
%
%\url{https://goo.gl/3N8n99}

\section{Results}
%\subsection*{Data Partition}
The data were randomly divided into three sub-samples, the first was used for the
estimation of the parameters of the neural network model (training set), the second was used to choose the model with more generalization capability (validation set) and the last was
used to evaluate how well the model generalize outside of the data set used for estimation (test set).

@@

% Falta poner que despues de pasarlo al geotiff se utilizo el software 
% ILWIS o el que se tuvo que usar y que posteriormente se genero el 
% map of landslide hazard mostrado en la figura  
% valorizar si se pone el codigo fuente

%The map of landslide hazards is showed in the figure \ref{fig:img02}.
%
% \begin{center}
%  \begin{figure}[H]
%   \centering
%   \includegraphics[scale=0.40]{img02}
%   \caption{\small{Map of landslide hazards}}
%   \label{fig:img02}
%  \end{figure}
% \end{center}

@@

%%% Alex's Discussion

The results obtained through geostatistical methodology met the assumptions for kriging method application. Final map of landslide probability of occurrence (see Fig. \ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work which implied an intense geological analysis (i.e. MARN inventory of 4792 landslides) together with the use of sophisticated statistical techniques. This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on. 
\begin{center}
%  \begin{figure}[H]
  \begin{figure}
   \centering
   \includegraphics[scale=0.73]{MASS_mapa_2}
   \caption{\small{Landslide hazard map MASS where the landslide probability of occurrence is shown.}}
   \label{fig:mass02}
  \end{figure}
 \end{center}
High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials. Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $mts^{3}$ that can affect large zones of urban areas. Southern areas of MASS also implies a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 m3 \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.

>>>>

\section{Results}
The data were randomly divided into three sub-samples, the first was used for the
estimation of the parameters of the neural network model (training set), the second was used to choose the model with more generalization capability (validation set) and the last was
used to evaluate how well the model generalize outside of the data set used for estimation (test set).

@@

@@

The results obtained through geostatistical methodology met the assumptions for kriging method application. Final map of landslide probability of occurrence (see Fig. \ref{fig:mass02} ) generated by kriging method was the result of multidisciplinary work which implied an intense geological analysis (i.e. MARN inventory of 4792 landslides) together with the use of sophisticated statistical techniques. This landslide hazard map is a user-friendly tool to evaluate landslide risk in MASS and can be useful for many purposes such as territorial planning, prevention and landslide mitigation and so on. 
\begin{center}
  \begin{figure}
   \centering
   \includegraphics[scale=0.73]{MASS_mapa_2}
   \caption{\small{Landslide hazard map MASS where the landslide probability of occurrence is shown.}}
   \label{fig:mass02}
  \end{figure}
 \end{center}
High probability of landslide occurrence in Picacho slope implies very high risk due the proximity of urban areas and due the large volume of mobilized materials. Major et al.\cite{major2004} identified in San Salvador volcano lahars as voluminous as 2 million of $mts^{3}$ that can affect large zones of urban areas. Southern areas of MASS also implies a high risk because landslides, similar to Las Colinas landslide which involved a total volume of around 200,000 m3 \cite{evans}, can occur in northern slope of Balsamo range and San Jacinto Hill affecting very crowded urban areas.
